### 2023-06-19 paper/sec-dis-pseudodata.tex
more work on sect 2

 As we discuss below, the calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors requires two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 In this section, we summarise the main features of each of the ongoing and future
 far-forward detectors considered in this study, in particular concerning
 their acceptance, geometry, and neutrino detection method.
 %
 We also indicate the expected performance of the three FPF detectors
 and how this translates into the dominant experimental systematic
 uncertainties.

\subsection{DIS pseudo-data generation}
\label{sec:pseudo-data_generation}

@@

\subsection{Systematic Effects on Pseudodata}
We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space. For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by

@@

\subsection{Experimental acceptance performance}

\paragraph{AdvSND} 
\begin{itemize}
    \item The detectors will be able to track muons that have energy greater
    than $20~\rm{GeV}$ (the values for the other charged leptons remain to be
    determined) with an acceptance angle of 100 mrad for the muons and 
    500 mrad for the both electrons and tau.
    \item In addition, the information on the charge of the outgoing leptons
    can also be accessed.
    \item It should also be possible to reconstruct the hadronic final states
    by measuring the total energy.
\end{itemize}

\paragraph{FLArE}
\begin{itemize}
    \item The detectors will be able to detect electrons with energy up to
    $1~\rm{TeV}$ and an acceptance angel as high as 0.5 rad. For the muons,
    the detectors will only be able to track them up to $1.5~\rm{GeV}$ with
    a scattering angle reaching up to 0.4 mrad. The reconstruction of the
    tau's angle and energy instead will be very difficult. However, it might
    be possible to find the vertex of a particular tau decay if fine position
    resolution is achieved.
    \item With the current baseline design of the detector, it will not be
    possible to access the information on the sign of the charged leptons.
    \item It should also be possible to reconstruct the hadronic final
    states but the reconstruction efficiency and particles will depend on
    the type of particles. It is expected that the final states hadrons will
    be dominated by pions, protons, and neutrons.
    \item Regarding the systematic errors on the charged lepton energy and
    scattering angle, it is expected to get $5\%$ energy resolution for
    electrons and about 15 mrad in angular resolution. Due to the large
    missing energy in the detector, $30\%$ energy resolution is probably
    achievable for muons with about 5 mrad angular resolution.
\end{itemize}

>>>>

 As we discuss below, the calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors requires two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 In this section, we summarise the main features of each of the ongoing and future
 far-forward detectors considered in this study, in particular concerning
 their acceptance, geometry, and neutrino detection method.
 %
 We also indicate the expected performance of the three FPF detectors
 and how this translates into the dominant experimental systematic
 uncertainties.
 %
 Since for the projection studies considered in this work we focus on muon
 neutrino scattering, we will focus the subsequent discussion on the detection
 performance of this neutrino flavour.

 Table~\ref{tab:FPF_experiments} indicates
 the rapidity coverage, target material,
 muon neutrino acceptance, and the identification and reconstruction performance
 for each of the far-forward LHC neutrino experiments considered
 in this work.
 %
 More details of the information listed in this table is provided
 in the following.

  %-----------------------------------------------------------------
\begin{table}[h!]
  \centering
  \small
  \renewcommand{\arraystretch}{1.60}
\begin{tabularx}{\textwidth}{Xcccc}
\toprule
Detector &  Rapidity &  Target &  Acceptance  & Performance \\
\midrule
FASER$\nu$  &   &     &       &              \\
SND@LHC  &   &     &       &              \\
\midrule
FASER$\nu$2  &   &     &       &              \\
AdvSND  &   &     &       &              \\
FLArE  &   &     &       &              \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work we indicate their rapidity coverage, target material,
  muon neutrino acceptance, and the identification and reconstruction performance.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

 \paragraph{AdvSND.}
 %
 The AdvSND far-detector will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad with information on the charge
 of the  outgoing charged leptons.
 %
 The total energy of the hadronic final state can also be measured.
 %
 A proposed ``near-detector'' companion is being discussed for AdvSND, but
 it would not be installed in the FPF and hence is not discussed here further.

 \paragraph{FLArE.}
 %
 A liquid argon (LAr) detector able to track muon neutrinos
 with energies  $E\le 1.5~\rm{TeV}$ with
 a scattering angle reaching up to 0.4 mrad.
 %
 No information on the sign of the charged leptons can be extracted.
 %
 Reconstruction of the total energy of the hadronic final state should be
 possible. 
 %
 A $\delta E_\nu\sim$30\% of energy resolution is
 the target performance for muons, with an associated
 $\delta \sim 5$ mrad of angular  resolution.

 % Table coverage + detector performance

\subsection{Differential event rate calculation}
\label{sec:pseudo-data_generation}

@@

\subsection{Estimating systematic uncertainties}

We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space. For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by

@@
